---
title: Demo
weight: 1
output: hugodown::md_document
---

## Snapshot testing

[testthat snapshot testing vignette](https://testthat.r-lib.org/articles/snapshotting.html).

* Add an error snapshot test for `get_packages2()`.

```{r eval=FALSE}
test_that("get_packages2 errors well", {
  withr::local_envvar("SECRET_PLANET_TOKEN" = "")
  expect_snapshot_error(get_packages2("maelle"))
})
```

* Modify the [error message](https://style.tidyverse.org/error-messages.html), re-run the test.

## Custom skipper

[testthat skipping vignette](https://testthat.r-lib.org/articles/skipping.html)

* Add custom skipper in `setup.R` (or another testthat helper file)

```{r eval=FALSE}
skip_if_not_beyonce <- function() {
  user <- whoami::username()
  if (user == "beyonce") {
    return(invisible(TRUE))
  }
  skip("Not Beyonce !")
}
```

* Use it in a new test

```{r eval=FALSE}
test_that("get_packages() works", {
  skip_if_not_beyonce()
  vcr::use_cassette("blabla", {
    pkgs <- get_packages("maelle")
  })
  expect_vector(pkgs, character())
})
```

* BACK TO SLIDES.

## Scheduled CI run with real requests

* Add secret to GitHub repo.

* Adding a workflow with scheduled weekly runs with vcr turned off.


```yaml
# For help debugging build failures open an issue on the RStudio community with the 'github-actions' tag.
# https://community.rstudio.com/new-topic?category=Package%20development&tags=github-actions
on:
  push:
    - main
  schedule:
    - cron:  '0 12 * * *'

name: R-CMD-check

jobs:
  R-CMD-check:
    runs-on: ${{ matrix.config.os }}

    name: ${{ matrix.config.os }} (${{ matrix.config.r }})

    strategy:
      fail-fast: false
      matrix:
        config:
          - {os: windows-latest, r: 'release'}
          - {os: macOS-latest, r: 'release'}
          - {os: ubuntu-20.04, r: 'release', rspm: "https://packagemanager.rstudio.com/cran/__linux__/focal/latest"}
          - {os: ubuntu-20.04,   r: 'devel', rspm: "https://packagemanager.rstudio.com/cran/__linux__/focal/latest", http-user-agent: "R/4.1.0 (ubuntu-20.04) R (4.1.0 x86_64-pc-linux-gnu x86_64 linux-gnu) on GitHub Actions" }

    env:
      R_REMOTES_NO_ERRORS_FROM_WARNINGS: true
      RSPM: ${{ matrix.config.rspm }}
      GITHUB_PAT: ${{ secrets.GITHUB_TOKEN }}
      VCR_TURN_OFF: true
      SECRET_PLANET_TOKEN: ${{ secrets.SECRET_PLANET_TOKEN }}

    steps:
      - uses: actions/checkout@v2

      - uses: r-lib/actions/setup-r@v1
        with:
          r-version: ${{ matrix.config.r }}

      - uses: r-lib/actions/setup-pandoc@v1

      - name: Query dependencies
        run: |
          install.packages('remotes')
          saveRDS(remotes::dev_package_deps(dependencies = TRUE), ".github/depends.Rds", version = 2)
          writeLines(sprintf("R-%i.%i", getRversion()$major, getRversion()$minor), ".github/R-version")
        shell: Rscript {0}

      - name: Restore R package cache
        uses: actions/cache@v2
        with:
          path: ${{ env.R_LIBS_USER }}
          key: ${{ runner.os }}-${{ hashFiles('.github/R-version') }}-1-${{ hashFiles('.github/depends.Rds') }}
          restore-keys: ${{ runner.os }}-${{ hashFiles('.github/R-version') }}-1-

      - name: Install system dependencies
        if: runner.os == 'Linux'
        run: |
          while read -r cmd
          do
            eval sudo $cmd
          done < <(Rscript -e 'writeLines(remotes::system_requirements("ubuntu", "20.04"))')

      - name: Install dependencies
        run: |
          remotes::install_deps(dependencies = TRUE)
          remotes::install_cran("rcmdcheck")
        shell: Rscript {0}

      - name: Check
        env:
          _R_CHECK_CRAN_INCOMING_REMOTE_: false
        run: |
          options(crayon.enabled = TRUE)
          rcmdcheck::rcmdcheck(args = c("--no-manual", "--as-cran"), error_on = "warning", check_dir = "check")
        shell: Rscript {0}

      - name: Upload check results
        if: failure()
        uses: actions/upload-artifact@main
        with:
          name: ${{ runner.os }}-r${{ matrix.config.r }}-results
          path: check
```


* [Line of a workflow file only enabling a job for push & internal PRs](https://github.com/r-lib/pkgdown/blob/900ef5471576f8f29508a7e7d94fae51390f2d96/.github/workflows/pkgdown.yaml#L15).

* BACK TO SLIDES.